Hydra battles in Coq

### 2020-09-02 latex/chapter-hydras.tex
new table of notations
table of notations
minor corrections

For this purpose, we define two mutual \emph{ad-hoc}  inductive types, where \texttt{Hydra} is the main type, and \texttt{Hydrae} is a helper for describing finite sequences of hydra.
\index{Types!Hydra}

@@

\index{Predicates!round}

\begin{Coqsrc}
Definition round h h' := exists n,  round_n n h h'.

@@

@@

\index{Notations!''-+->''}
\index{Notations!''-*->''}

@@

\vspace{4pt}
\emph{From Module~\href{../src/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\index{Coq!Type classes}

@@

\begin{Coqsrc}
Fixpoint iterate {A:Type} (f : A -> A) (n:nat) (x: A) :=
 match n with 
  | 0 => x
  | S p => f (iterate f p x)
 end.
\end{Coqsrc}

>>>>

For this purpose, we define two mutual \emph{ad-hoc}  inductive types, where \texttt{Hydra} is the main type, and \texttt{Hydrae} is a helper for describing finite sequences of hydra.
\label{types:Hydra}
\label{types:Hydrae}

@@

\index{Predicates!round}
\label{sect:infix-round}
\begin{Coqsrc}
Definition round h h' := exists n,  round_n n h h'.

@@

\label{sect:infix-rounds}

@@

@@

\vspace{4pt}
\emph{From Module~\href{../src/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}
\index{Coq!Type classes}
\label{types:Battle}

@@

The functional \texttt{iterate}, similar to Standard Library's \texttt{Nat.iter},
is defined and studied in~\href{../src/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}).

\label{Functions:iterate}

\begin{Coqsrc}
Fixpoint iterate {A:Type}(f : A -> A) (n: nat)(x:A) :=
  match n with
  | 0 => x
  | S p => f (iterate  f p x)
  end.
\end{Coqsrc}

### 2020-09-02 latex/hydras.tex
minor corrections

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{makeidx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\setcounter{tocdepth}{2}
\input{coqmacros}

@@

\section{Index}
Some notations may belong to several scopes. For instance, ``\texttt{o<}'' is
bound in \texttt{ON\_scope}, \texttt{E0\_scope}, \texttt{t1\_scope}, etc., and locally in several libraries.

\subsection{Infix notations}

\vspace{4pt}

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & Ordinal addition & \pageref{sect:infix-oplus} \\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\

@@

\subsection{Other notations}

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega},\dots\\
phi0     & \texttt{phi0 alpha} & $\varphi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\

@@

>>>>

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{makeidx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{threeparttable}
\setcounter{tocdepth}{2}
\input{coqmacros}

@@

\section{Index}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main types and type classes}
\begin{tabular}{|c|c|c|l|}
\hline
Name & Description& Page \\\hline
Battle & Type class of battle types & \pageref{types:Battle} \\
E0 & (Well formed) ordinals below $\epsilon_0$ & \pageref{types:E0}\\
Hvariant & variants for proving terminatio of hydra battles & \pageref{sect:hvariant-def} \\
Hydra & tree-like representation of hydras & \pageref{types:Hydra} \\
Hydrae & finite sequences of hydras & \pageref{types:Hydrae} \\
ON & ordinal  notations & \pageref{types:ON} \\
ON\_for & comparison of an ordinal notation with Schütte's model &  \pageref{types:ON-for}\\
ON\_iso & isomorphism of ordinal notations  & \pageref{types:ON-iso}\\

Ord & countable ordinals (after Schütte) & \pageref{types:Ord} \\
ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
SubON & comparison of ordinal notations & \pageref{types:SubON} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
WO & well orders (Schütte's definition) & \pageref{types:WO} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Main functions}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& Canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& Helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
iterate & iterate $f$ $n$ $x$ & $f^{(n)}(x)$ & Functional iteration & \pageref{Functions:iterate} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\vspace{4pt}
\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Infix notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality \tnote{1} & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & Ordinal addition & \pageref{sect:infix-oplus} \\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\

@@

\begin{tablenotes}
 \item [1]
Some notations may belong to several scopes. For instance, ``\texttt{o<}'' is
bound in \texttt{ON\_scope}, \texttt{E0\_scope}, \texttt{t1\_scope}, etc., and locally in several libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Other notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
F & \texttt{F $n$} & $n$ & The $n$-th finite ordinal &  
\pageref{sect:notation-F}, \pageref{sect:notation-F-sch}\\ 
FS & \texttt{FS $n$} & $n+1$ & The $n+1$-th finite ordinal  \tnote{2} &  
\pageref{sect:notation-FS}\\ 
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega}, \pageref{sect:omega-T1}, \pageref{sect:omega-notation2}, \dots\\
phi0     & \texttt{phi0 alpha} & $\varphi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\

@@

\begin{tablenotes}
  \item [2] Note that there exist also various coercions from \texttt{nat} to types of ordinal. Depending on the current scope and  \coq's syntactic analysis algorithm, \texttt{F} may be left implicit.
\end{tablenotes}
  \end{threeparttable}

\end{table}
